$3$-D Weak Lensing Mass Map Reconstruction: Reducing the line of sight smearing

### 2020-12-06 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex
small changes

\begin{figure*}
 \centering
 \includegraphics[width=1.0\textwidth]{peak_histograms_NFW.pdf}
 \caption{The number per square degree histograms of detected peak values from
     all of the simulations.  The solid red steps result from reconstructions
     with the NFW dictionary penalized with different regularization
     parameters: $\lambda=3.5,4.0,5.0$. The dashed blue steps are the
     corresponding results of the reconstructions from $1000$ realizations of
     pure noise fields. The gray lines are the best-fit Gaussian distributions
     to the noises' peak histograms.
    }\label{fig_peakHist}
\end{figure*}

Following \citet{WL-massMap-Glimpse2D-Lanusse2016}, we normalize detected peaks
in the $l$-th lens redshift plane to account for the peak amplitude difference
due to the difference in the norm of the lensing kernels for different redshift
bins:
\begin{equation}
\delta^{\rm{n}}_{\rm{peak}}(\vec{\theta},z_l)=\delta_{\rm{peak}}(\vec{\theta},z_l)/\mathcal{R}_{l}^{\frac{1}{2}},
\end{equation}
where the normalization matrix is defined as
\begin{equation}
\mathcal{R}_{l}=\sum_s K^2(z_l,z_s).
\end{equation}
The solid steps in Figure \ref{fig_peakHist} show the histograms for the
normalized peaks with different penalization parameters. Also, we simulate
$1000$ realizations of pure noise fields and perform the reconstructions on
these noise fields to study the noise properties. The dashed steps in Figure
\ref{fig_peakHist} show the histograms of normalized peaks detected from the
pure noise fields. The solid lines in Figure \ref{fig_peakHist} show the
best-fit Gaussian distributions to the noise peaks' histograms.

@@

We select peaks with values greater than an ad-hoc threshold as candidates of
galaxy clusters following \citet{HSC1-massMap-cluster}.  The threshold is set
to a few times the standard deviation of the noise peaks. We use different
detection thresholds ($1.5\sigma$ and $3.0\sigma$) to detect galaxy clusters
from the mass maps reconstructed with $\lambda=3.5,4.0,5.0$. The left and
middle columns of Figure \ref{fig_detFalsRateNFW} show the detection rates for
halos in the (mass, redshift) planes with detection thresholds set to
$1.5\sigma$ and $3.0\sigma$ of the noise field, respectively. The right column
of Figure \ref{fig_detFalsRateNFW} shows the corresponding numbers of false
detections per square degree as functions of detection thresholds. The first,
second, and third rows of Figure \ref{fig_detFalsRateNFW} correspond to the
$lambda=3.5,4.0,5.0$, respectively.

@@

\begin{figure*}
 \centering
 \includegraphics[width=1.0\textwidth]{detfalse_threshold_NFW_lbd35.pdf}
 \includegraphics[width=1.0\textwidth]{detfalse_threshold_NFW_lbd40.pdf}
 \includegraphics[width=1.0\textwidth]{detfalse_threshold_NFW_lbd50.pdf}
 \caption{The detection rate and false peak density for different $\lambda$ and
     detection thresholds. The first, second, and third rows correspond to the
     results with $lambda=3.5,4.0,5.0$, respectively. The left and middle columns
     are the halo detection rates for detection thresholds equal $1.5\sigma$ and
     $3.0\sigma$, respectively. The right column is the density of false peaks as
     a function of detection threshold.
    } \label{fig_detFalsRateNFW}
\end{figure*}

>>>>

\begin{figure*}
 \centering
 \includegraphics[width=1.0\textwidth]{peak_histograms_NFW.pdf}
 \caption{The number per square degree histograms of detected peak values from
     all of the simulations.  The solid red steps result from reconstructions
     with the NFW dictionary penalized with different regularization
     parameters: $\lambda=3.5,4.0,5.0$. The dashed blue steps are the
     corresponding results of the reconstructions from $1000$ realizations of
     pure noise catalogs. The gray lines are the best-fit Gaussian distributions
     to the noises' peak histograms.
    }\label{fig_peakHist}
\end{figure*}

Following \citet{WL-massMap-Glimpse2D-Lanusse2016}, we normalize the detected
peaks in the $l$-th ($l=1...20$) lens redshift plane to account for the peak
amplitude difference due to the difference in the norm of the lensing kernels
for different redshift bins:
\begin{equation}
\delta^{\rm{n}}_{\rm{peak}}(\vec{\theta},z_l)=\delta_{\rm{peak}}(\vec{\theta},z_l)/\mathcal{R}_{l}^{\frac{1}{2}},
\end{equation}
where the normalization matrix is defined as
\begin{equation}
\mathcal{R}_{l}=\sum_s K^2(z_l,z_s).
\end{equation}
The solid steps in Figure \ref{fig_peakHist} show the histograms of the
normalized peaks with different penalization parameters. Also, we simulate
$1000$ realizations of pure noise catalogs and perform the reconstructions on
these noise catalogs to study the noise properties. The dashed steps in Figure
\ref{fig_peakHist} show the histograms of normalized peaks detected from the
pure noise catalogs. The solid lines in Figure \ref{fig_peakHist} show the
best-fit Gaussian distributions to the noise peaks' histograms.

@@

We select peaks with values greater than an ad-hoc threshold as candidates of
galaxy clusters following \citet{HSC1-massMap-cluster}.  The threshold is set
to a few times the standard deviation of the noise peaks. We use different
detection thresholds ($1.5\sigma$ and $3.0\sigma$) to detect galaxy clusters
from the mass maps reconstructed with $\lambda=3.5,4.0,5.0$. The left and
middle columns of Figure \ref{fig_detFalsRateNFW} show the detection rates for
halos in the (mass, redshift) planes with detection thresholds set to
$1.5\sigma$ and $3.0\sigma$ of the noise peaks' distributions, respectively.
The right column of Figure \ref{fig_detFalsRateNFW} shows the corresponding
numbers of false detections per square degree as functions of detection
thresholds. The first, second, and third rows of Figure
\ref{fig_detFalsRateNFW} correspond to the $lambda=3.5,4.0,5.0$, respectively.

@@

\begin{figure*}
 \centering
 \includegraphics[width=1.0\textwidth]{detfalse_threshold_NFW_lbd35.pdf}
 \includegraphics[width=1.0\textwidth]{detfalse_threshold_NFW_lbd40.pdf}
 \includegraphics[width=1.0\textwidth]{detfalse_threshold_NFW_lbd50.pdf}
 \caption{The detection rates and false peak densities for different
     penalization parameters and detection thresholds. The first, second, and
     third rows correspond to the results with $\lambda=3.5,4.0,5.0$,
     respectively. The left and middle columns are the halo detection rates for
     detection thresholds equal $1.5\sigma$ and $3.0\sigma$, respectively. The
     right column shows the density of false peaks as a function of detection
     threshold.
    } \label{fig_detFalsRateNFW}
\end{figure*}
